### 2015-05-17 Manuscript/Missing_mammals-draft.tex
Updated intro

%But missing data in living taxa problem
However, the Total Evidence method requires, by definition, a lot of data. One must collect both molecular data for living taxa as well as morphological data for both living and fossil taxa, two types of data that require fairly different technical skills (e.g. \cite{meredithimpacts2011} \textit{vs.} \cite{O'Leary08022013}). Additionally, entire sections of this data can sometimes be difficult or impossible to collect for every taxa present in the analysis. For example, fossil have really rarely molecular data available and morphological characters are rarely collected when molecular data is available. Therefore, the ability of the Total Evidence method to recover correct topology is expected to decrease when there is a low overlap between the living and the fossil data \cite{GuillermeCooper}. The effect of missing data is most important on topology when too few living taxa have available morphological data \cite{GuillermeCooper}. For example, if there is no morphological available for any living taxa within an entire clade, it is impossible to link a fossil taxon to this clade because no morphological data will overlap between the fossil (regardless the amount of data available for the fossil) and the living taxa (that have no morphological data). This property of the Total Evidence method can rapidly lead to important topological incongruities because the fossil will only be able to branch to a clade of living taxa that contains morphological data, even if in reality, the fossil taxon does not belong to that clade \cite{GuillermeCooper} (see figure ~\ref{Figure_missing_data_problem}).

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{MissingDataFigure.pdf}
\caption{Example of topological errors due to missing morphological data in living taxa. If a phylogeny contains two clades, for example Proboscidea and Cetartiodactyla, with molecular data for both (in grey) but only morphological data for Proboscidea only (in red). If an additional Cetartiodactyla fossil (with no molecular data) is added to the phylogeny, it will erroneously branch with the Proboscidea clade instead of the Cetartiodactyla one because no morphological data will overlap between the fossil Cetartiodactyla and the living ones.}
\label{Figure_missing_data_problem}
\end{figure}

>>>>

%But missing data in living taxa problem
However, the Total Evidence method requires, by definition, a lot of data. One must collect both molecular data for living taxa as well as morphological data for both living and fossil taxa, two types of data that require fairly different technical skills (e.g. \cite{meredithimpacts2011} \textit{vs.} \cite{O'Leary08022013}). Additionally, entire sections of this data can sometimes be difficult or impossible to collect for every taxa present in the analysis. For example, fossil have really rarely molecular data available and morphological characters are rarely collected for living taxa when molecular data is available (e.g. \cite{slaterphylogenetic2013,beckancient2014}). This difference between both data can lead to topological errors in phylogenetic inference \cite{GuillermeCooper}. In fact, the ability of the Total Evidence method to recover correct topology is expected to decrease when there is a low overlap between morphological data from the living and the fossil taxa \cite{GuillermeCooper}. The effect of missing data is most important on topology when too few living taxa have available morphological data \cite{GuillermeCooper}. For example, if there is no morphological available for any living taxa within an entire clade, it is impossible to link a fossil taxon to this clade because no morphological data will overlap between the fossil (regardless the amount of data available for the fossil) and the living taxa (that have no morphological data). This property of the Total Evidence method can rapidly lead to important topological incongruities because the fossil will only be able to branch to a clade of living taxa that contains morphological data, even if in reality, the fossil taxon does not belong to that clade \cite{GuillermeCooper} (see figure ~\ref{Figure_missing_data_problem}).

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{MissingDataFigure.pdf}
\caption{Example of topological errors due to missing morphological data in living taxa. If a phylogeny contains two clades, for example Aves and Mammalia, with molecular data (in grey) for both but only morphological data (in red) for Aves. If an additional Mammalia fossil (with no molecular data) is added to the phylogeny, it will erroneously branch with the Aves clade instead of the Mammalia one because no morphological data will overlap between the fossil Mammalia and the living ones.}
\label{Figure_missing_data_problem}
\end{figure}
